Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
some work with the flow

Fuel cycle simulations, as any simulation process, do not produce results
without errors. Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplification made by the simulator) and the
``functional`` uncertainty (uncertainty on the operation parameters of the
different facilities).

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.

\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a simple
transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with \glspl{MOX}, consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
\end{figure}

@@

Indeed the transition scenario has been design to allow all the reactors to
receive the fuel as needed allowing them to be producing power all the time.
This ensure that the uncertainty measured on other parameters are not influence
by the reactors miss-loadings.

@@

\subsection{Natural Uranium Consumption}

Figure \ref{fig:unat_full} represents the cumulative natural uranium
consumption as a function of time. The uncertainty on the cumulative uranium
consumption grows as expected with the time and the loading of the \glspl{LWR}.
The increase stops around year 125y with the decommissioning of the last
\glspl{LWR}.

@@

The fluctuation of the full relative uncertainty at low time are because of the
sensitivity to the fuel loading: all reactors at the beginning have synchronised
cycle, this phenomenon disappears with the gradual decommissioning of the initial
reactor, spread on 50 years.

@@

As expected, cooling time, separation efficiency and thermal power does not
affect the natural uranium consumption.  The uncertainty on the natural uranium
consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
length is, the more fuel will be loaded.

As the number of deployed \glspl{LWR} reactors increases, as each parameters is
sampled once for each facilities, the average length of the cycle (as well as
the number of loaded batches) converges to the reference value.
The fuel enrichment contribution follow a smoother behavior, so as the total
relative uncertainty decrease, their contribution increases over time.

\subsection{Fissile Inventory}
As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
year 40, with the deployment of the first reprocessing facility. It grows
during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
When he steady state is reached (full \glspl{FBR} fleet), the plutonium
inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
than the deployment needs.

@@

Regarding the uncertainty, beside the low inventory artefact observable around
year 40, the relative uncertainty starts at about $5\%$, and grows until year
125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
it will reach an equilibrium between $5$ and $10\%$...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length, as for the uranium needs, lower cycle length
implies more fuel loads. Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
to lack, and the availability of the used fuel starts to dictate the evolution
of fissile in storage. The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.

@@

It is also interesting to note that, the uncertainty contribution from the cycle
length are conversion toward the power contribution, such as the increase of
fuel loads effect tends to vanish and let its place to a discharge burnup
effect (the power uncertainty only affects the burnup of the fuel at discharge).

@@

Even if for the two output metric analysed there is no surprise such as the
identified uncertainty contributions, it is very interesting to be able to
measure them and rank them.

In this study, we can estimate than the cycle length uncertainty of $10\%$
varies from $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
on the enrichment implies a almost flat uncertainty of $2\%$, and the enrichment
tails uncertainty have an even lower contributions of $1\%$.

It is also very interesting to observe that while the plutonium inventory uncertainty
reach a pick at $30\%$, lead by the cooling time uncertainty contribution, the reactor
parameters seems to have a lower contribution, the cycle time contribution
picking at $10\%$ and stabilizing with the power contribution around $1\%$

@@

Secondly, it is important to note the special character of the time related
parameters uncertainty in a fuel cycle study, such as cooling time and cycle
length. As the cycle length impact the discharge fuel burnup, it also affects
the frequency of the fuel loads, this, as well as the cooling may imply a
uncertainty on the material availability, which could lead to a large
uncertainty. Those kind of uncertainties will need a special treatment on further
uncertainty analysis.

>>>>

Fuel cycle simulations, as any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplification made by the simulator) and the
``operational`` uncertainty (uncertainty on the operation parameters of the
different facilities).

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation.  In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to a fuel enrichment uncertainty close to
$10\%$.

\subsection{The Fuel Cycle}
This work aims to assess the impact of the operational uncertainties of a simple
transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel.  The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with \glspl{MOX}, consisting of plutonium blended with natural
uranium.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}
    \label{fig:power}
\end{figure}

@@

Indeed the transition scenario has been design to allow all the reactors to
receive the fuel as needed allowing them to be producing power all the time.
This ensures that the uncertainty measured any other parameters is not
influenced by the reactors miss-loadings.

@@

\subsection{Natural Uranium Consumption dedicated to PWR-UOX fabrication}

Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
dedicated to PWR-UOX fuel fabrication as a function of time.  The uncertainty on
the cumulative uranium consumption grows as expected with the time and the
loading of the \glspl{LWR}.  The increase stops around year 125y with the
decommissioning of the last \glspl{LWR}.

@@

The fluctuation of the full relative uncertainty at low time are induced by the
fuel loading: all reactors at the beginning of the simulation have synchronised
cycle, this phenomenon disappears with the gradual decommissioning of the
initial reactors, spread on 50 years.

@@

As expected, cooling time, separation efficiency and thermal power don't
affect the natural uranium consumption.  The uncertainty on the natural uranium
consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
length is, the more fuel will be loaded.

With the increase of deployed reactors, the number of batches of \glspl{PWR}
fuel loaded converges to the references one (a random cycle length
values if randomly determined for each deployed reactors), reducing its impact
on the uncertainty on the total uranium consumption.
The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, its
relative contribution increases over time.

\subsection{Fissile Inventory}
The fissile inventory corresponds to the amount on separated fissile waiting to
be blend with natural uranium in order to produce the \glspl{FBR} MOX fuel.

As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
year 40, with the deployment of the first reprocessing facility.  It grows
during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
When he steady state is reached (full \glspl{FBR} fleet), the plutonium
inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
than the deployment needs.

@@

Regarding the uncertainty, beside the low inventory artefact observable around
year 40, the relative uncertainty starts at about $5\%$, and grows until year
125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
it would have reached an equilibrium between $5$ and $10\%$ with longer
simulations...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length, as for the uranium needs, lower cycle length
implies more fuel loads.  Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
to lack, and the availability of the used fuel starts to dictate the evolution
of fissile in storage.  The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.

@@

It is also interesting to note that, the uncertainty contribution from the cycle
length is between year 40 and 70 comes mainly from fuel batch loading
frequencies, and after it relative contributions follows closely the thermal
power one, suggesting a contributions through fuel discharge burnup (i.e. fuel
discharge composition).

@@

Uranium consumption and separated fissile inventory are two important metrics
regarding to non proliferation and nuclear archaeology. In this study, we have
been able to estimate than the cycle length uncertainty of $10\%$ implies a
variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
on the enrichment implies a almost flat uncertainty of $2\%$.

Regarding the reprocessed fissile inventory, this study has shown the limited
impact of the reprocessed fuel compositions (through burnup variations) it
limited to $5\%$, where fuel availability constrains, fuel loading frequency (cycle
time), or fissile materials available for fuel fabrication (cooling time) can lead to higher
uncertainties, respectively up to $10\%$ and to $30\%$. Moreover it is very
interesting to observe the pressure transition from one to the other around
year 70.

@@

Secondly, it is important to note the special character of the time related
parameters uncertainty in a fuel cycle study, such as cooling time and cycle
length. Where some of those time related parameter will on the first order only
impact material availability (as the cooling time will do), some other, like
cycle length, will also have a impact as physical parameters such as fuel enrichment or thermal
power.

Those time related parameters can not only impact the uncertainty as
physical parameters (for example the cycle lenght impacting the fuel discharge
burnup and composition)

Cycle length impacts the discharge fuel burnup, it also affects
the frequency of the fuel loads, this, as well as the cooling may imply a
uncertainty on the material availability, which could lead to a large
uncertainty.  Those kind of uncertainties will need a special treatment on further
uncertainty analysis.
